Meta-analysis

### 2019-09-02 05_MetaAnalysis.Rmd
Remove analysis with fungicide subset, it was incorrect

PM_MB_means_T <- PM_MB_means %>%
   group_by(Trial_ref, Fungicide) %>%
   summarise(trial_mean = mean(grain_yield.t.ha.,na.rm = TRUE),
             BW_trial_variance = sd(grain_yield.t.ha.,na.rm = TRUE)^2)
PM_MB_means_T

summary(lm(BW_trial_variance ~ trial_mean  Fungicide, data = PM_MB_means_T))
summary(lm(BW_trial_variance ~ trial_mean, data = subset(PM_MB_means_T, Fungicide == "Tebeconazole")))
summary(lm(BW_trial_variance ~ trial_mean, data = subset(PM_MB_means_T, Fungicide == "propiconazole")))

@@

lm_within <- lm(BW_trial_variance ~ trial_mean * Trial_ref + Fungicide,
                    data = PM_MB_means_T)
summary(lm_within) # Not accurate in predicting TrialVariance from trial means

lm_within2 <- lm(BW_trial_variance ~ trial_mean + Trial_ref + Fungicide,
                    data = PM_MB_means_T)
summary(lm_within2) # Not accurate in predicting TrialVariance from trial means

lmer_within_1 <- lmer(BW_trial_variance ~ trial_mean + (1|Trial_ref/Fungicide),
                    data = PM_MB_means_T)
# unable to nest Fungicide under trial ref

lmer_within_1 <- lmer(BW_trial_variance ~ trial_mean + Fungicide + (1|Trial_ref),
                    data = PM_MB_means_T)
# not accurate  for predicting TrialVariance

summary(lmer_within_1)

>>>>

PM_MB_means_T <- PM_MB_means %>%
   group_by(Trial_ref) %>%
   summarise(trial_mean = mean(grain_yield.t.ha.,na.rm = TRUE),
             BW_trial_variance = sd(grain_yield.t.ha.,na.rm = TRUE)^2)
PM_MB_means_T

summary(lm(BW_trial_variance ~ trial_mean, data = PM_MB_means_T))
summary(lm(BW_trial_variance ~ trial_mean, data = subset(PM_MB_means_T, Fungicide == "Tebeconazole")))
summary(lm(BW_trial_variance ~ trial_mean, data = subset(PM_MB_means_T, Fungicide == "propiconazole")))

@@
